---
title: "p8105_hw1_sj2921.Rmd"
author: "Shan Jiang"
date: "9/13/2018"
output:
  github_document
---

# Problem 1
## Section 1.1
Here is a **Data Frame** to generate a sample of size 10 from a _uniform distribution_ of number ranges from 0-5, and a vector for choosing elements which are greater than 2:
```{r chunk_1.2.1}
library(tidyverse)
a = runif(10, min = 0, max = 5)
example_df = tibble(
  vec_numeric = a,
  vec_logical = c(a >= 2),
  vec_char = c("teacher","soldier", "doctor","kids","master","banker","hacker","servant ","accountant","statistician"),
  vec_factor = factor(c("Jan", "Feb", "Mar", "Apr", "May", "Jun", 
  "Jul", "Aug", "Sep", "Oct"))
)
```
The result of mean in each vector in data frame is shown below as an attempt: the output of **numeric vector and logical vector** works while for **character vector and factor vector**, it does not work. 
Since the data type of **character vector and factor vector** cannot be used for operations easily, so the mean of these two vectors are NAs.  
```{r chunk_1.2.2}
mean(example_df$vec_numeric)
mean(example_df$vec_logical)
mean(example_df$vec_char)
mean(example_df$vec_factor)
```


## Section 1.3 
Data Frame: Data Type coersion and Convertion
```{r chunk_1.3.1,include=FALSE}
as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```

```{r chunk_1.3.2}
as.numeric(as.factor(example_df$vec_char))
as.numeric(as.character(example_df$vec_factor))
```
# Problem 2

```{r chunk_5}
set.seed(2018)
Scatter_df = tibble(
         x = rnorm(1000),
         y = rnorm(1000),
         vec_lgc = x + y > 0,
         vec_num = c(as.numeric(vec_lgc)),
         vec_fac = factor(c(as.numeric(vec_lgc)))
         )
```
* The size of the dataset are that the rows are `r nrow(Scatter_df)` and the number of varibles are `r ncol(Scatter_df)`,
* The mean of x is `r mean(Scatter_df$x)`,
* The median of x is `r median(Scatter_df$x)`,
* The proportion of cases for which the logical vector is TRUE is `r sum(Scatter_df$vec_lgc == TRUE)` / `r nrow (Scatter_df)`

```{r chunk_6}
ggplot(Scatter_df, aes(x = x, y = y, color = vec_lgc)) + labs(title = "Graph1 vec_lgc ") + theme(plot.title = element_text(face = "bold", hjust = 0.5)) + geom_point()
ggsave("hw1_Scatter_1.png", width = 5,height = 6)
ggplot(Scatter_df, aes(x = x, y = y, color = vec_num)) + labs(title = "Graph2 vec_num ") + theme(plot.title = element_text(face = "bold", hjust = 0.5)) + geom_point()
ggplot(Scatter_df, aes(x = x, y = y, color = vec_fac)) + labs(title = "Graph3 vec_fac ") + theme(plot.title = element_text(face = "bold", hjust = 0.5)) + geom_point()

```

